---
title: "ENES 197: The Fault in Our Data"
# subtitle: "A General Education Course in Data Science"
date: "Summer Session II 2022"
author: "Dr. Brian Danielak"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3.5, fig.width=5, fig.align='center'}
library(dplyr)
library(ggplot2)
library(magrittr)
library(scales)

diamonds %>%
  ggplot(aes(carat, price, color = clarity)) +
  geom_point(alpha = 0.2) +
  facet_wrap( ~ cut, scales = "free_x") +
  theme_light() +
  scale_y_continuous(labels = scales::dollar_format()) +
  labs(
    caption = "Example: Comparing the size, price, and clarity of 50,000 diamonds"
  )

# mpg %>%
#   ggplot() +
#   geom_point(aes(cty, hwy, color = as.factor(trans))) +
#   facet_wrap(~ year) +
#   theme_light()
  
```

# Introducing **ENES 197**

ENES 197 teaches data science and computational thinking using the Python programming language. The course counts for both a Distributive Studies (DSSP) **Gen Ed** rfequirement and an **I-Series** (SCIS) requirement. ***No prior programming experience is necessary***.

## How Can Data Science Help Us?

-   How do we know when an entire city's water supply is poisoned?
-   How can we understand why only a few people are rich while so many others are in need?
-   How can we find patterns in 50,000 pieces of data?

## How Will the Course Be Offered?

This will be an entirely **online** course; you can participate from anywhere you have reliable internet access and access to a computer.

## Goals for the Course

-   Introduce students to basic programming concepts including variables, control flow, data structures, functions, and program design
-   Teach students how to wrangle and tidy the often messy data we get from real-world sources
-   Show students a "grammar of graphics" (Wilkinson, 1999) for data visualization
-   Have students create scriptable data analyses that can be run and verified by others
-   Use industry-standard data science tools for reproducible mathematical modeling, visualization, and communication (viz. Python, pandas, Numpy, SciPy, and JupyterLab).
